Enforced Invariant Confluence

### 2018-03-12 doc/paper_redux/stratified_iconfluence.tex
Added some TODOs for various examples.

>>>>

\begin{example}
  \todo{%
    Bank account example from~\cite{gotsman2016cause}. This might be hard to
    actually implement since the bank account merge is hard to do with a
    state-based object. This example only acquires a single lock.
  }
\end{example}

\begin{example}
  \todo{%
    Auction example from~\cite{gotsman2016cause}. I think we could automate
    this one. This one acquires a single lock. We don't need the lock once
    we're finalized.
  }
\end{example}

\begin{example}
  \todo{%
    Courseware application from~\cite{gotsman2016cause}. When course is
    non-empty, we can allow any operations at all. When a course is empty, we
    cannot allow concurrent operations on it. This one should hopefully be easy
    to automate.
  }
\end{example}

\begin{example}
  \todo{%
    Ad counter from~\cite{balegas2015putting}. This might be hard like the bank
    account balance. Adding numbers might be tricky in a state-based approach.
  }
\end{example}

\begin{example}
  \todo{%
    Tournament from~\cite{balegas2015putting}. This might be hard. Pretty
    complicated example with set cardinality constraints.
  }
\end{example}
